# Data visualization

[2.2.5](https://r4ds.hadley.nz/data-visualize.html#exercises)

1.
How many rows are in `penguins`?  
How many columns?

```{r}
library(palmerpenguins)
library(tidyverse)


```


2.
What does the `bill_depth_mm` variable in the `penguins` data frame describe?
Read the help for `?penguins` to find out.

3.
Make a scatterplot of `bill_depth_mm` vs. `bill_length_mm`.
That is, make a scatterplot with `bill_depth_mm` on the y-axis and `bill_length_mm` on the x-axis.
Describe the relationship between these two variables.

4.
What happens if you make a scatterplot of `species` vs. `bill_depth_mm`?
What might be a better choice of geom?

5.
Why does the following give an error and how would you fix it?

```{r}
#| eval: false
ggplot(data = penguins) + 
geom_point()
```

6.
What does the `na.rm` argument do in `geom_point()`?
What is the default value of the argument?
Create a scatterplot where you successfully use this argument set to `TRUE`.

7.
Add the following caption to the plot you made in the previous exercise: "Data come from the palmerpenguins package." Hint: Take a look at the documentation for `labs()`.

8.
Recreate the following visualization.
What aesthetic should `bill_depth_mm` be mapped to?
And should it be mapped at the global level or at the geom level?

[2.4.3](https://r4ds.hadley.nz/data-visualize.html#exercises-1)

1.  
Make a bar plot of `species` of `penguins`, where you assign `species` to the `y` aesthetic.
How is this plot different?

2.  
How are the following two plots different?
Which aesthetic, `color` or `fill`, is more useful for changing the color of bars?

```{r}
#| eval: false

ggplot(penguins, aes(x = species)) +
  geom_bar(color = "red")

ggplot(penguins, aes(x = species)) +
  geom_bar(fill = "red")
```

3.  
What does the `bins` argument in `geom_histogram()` do?

4.  
Make a histogram of the `carat` variable in the `diamonds` dataset that is available when you load the tidyverse package.
Experiment with different binwidths.
What binwidth reveals the most interesting patterns?
