# Workflow: basics

## [3.5](https://r4ds.hadley.nz/workflow-basics#exercises) {.unnumbered}

1.
> Why does this code not work?

```{r}
#| error: true

my_variable <- 10
my_varıable
```

The i is dotless in the call of my_variable and so doesn't match.

:::{.callout-note collapse=false appearance='default' icon=true}
## Quarto chunk `error: true`
In Quarto this chunk ran using `error: true` which shows the error in the book, useful for instances where code errors are shared in Quarto presentations or on websites!

:::

2.
> Tweak each of the following R commands so that they run correctly:

```{r}
#| eval: false

libary(todyverse)

ggplot(dTA = mpg) + 
  geom_point(maping = aes(x = displ y = hwy)) +
  geom_smooth(method = "lm)
```

Corrected:

```{r}
library(tidyverse)

ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy)) +
  geom_smooth(mapping = aes(x = displ, y = hwy),
              method = lm)
```

There are a lot of corrections needed in this code.
It includes:

- `todyverse` should be `tidyverse`)
- `dTA` instead of `data`)
- `maping` instead of `mapping`
- missing `,` between `x = displ` and `y = hwy`
- a `"` before `"lm` 

:::{.callout-note collapse=false appearance='default' icon=true}
## Quotations around the lm in `method =` (note)
`"lm"` will work but RStudio will flash up an error in the margin saying `unexpected token` if you click on the red circle with white cross.
:::

- `geom_smooth()` also requires its own mapping information as the `aes()` isn't available to that line. 
If this were global it would be:

```{r}
library(tidyverse)

ggplot(data = mpg, mapping = aes(x = displ, y = hwy)) + 
  geom_point() +
  geom_smooth(method = lm)
```

3.
> Press Option + Shift + K / Alt + Shift + K.
> What happens?

The keyboard shortcuts overlay menu comes up in RStudio.

> How can you get to the same place using the menus?

Tools/Keyboards Shortcuts Help

4.
> Let's revisit an exercise from the https://r4ds.hadley.nz/data-visualize#sec-ggsave.
> Run the following lines of code.

```{r}
#| eval: false
#| code-line-numbers: true

my_bar_plot <- ggplot(mpg, aes(x = class)) +
 geom_bar()
my_scatter_plot <- ggplot(mpg, aes(x = cty, y = hwy)) +
 geom_point()
ggsave(filename = "mpg-plot.png", plot = my_bar_plot)
```

> Which of the two plots is saved as `mpg-plot.png`?

The bar plot from the object `my_bar_plot` is saved.

> Why?

This has been explicitly detailed in the `ggsave()` function.
Both plots are also saved as objects (https://r4ds.hadley.nz/workflow-basics#sec-whats-in-a-name) so they can be referred to in the function.
